---
title: "Artificial Phantasia: Evidence for Propositional Reasoning-Based Mental Imagery Within Large Language Models"
author: "Author"
date: "August 28, 2025"
output: pdf_document
---

## Summary

This R Markdown document reproduces the analyses reported in [Author Names Removed for Anonymized Peer Review]. _Artificial Phantasia: Evidence for Propositional Reasoning-Based Mental Imagery Within Large Language Models_.

`Groundhog` will load the exact versions of the `R` packages used for the reported
analyses. However, it cannot control the version of `R` that you are running.
We used `\R 4.5.1`. `Groundhog` will load `tidyverse 2.0.0`, `knitr 1.50`,
and `patchwork 1.3.1`.

If you have issues with `groundhog` (authorizing in the console the creation of
a library folder when using groundhog for the first time is needed) or do not
want to use it, follow the instructions in the comment below.

```{r setup, include=FALSE}
library(knitr)
library(patchwork)
library(tidyverse)

# Set chunk options
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r data_loading}
llm_data_finke <- read.csv("output_csvs/llm_graded_results_finke.csv")
llm_data_novel <- read.csv("output_csvs/llm_graded_results_novel.csv")

human_data_finke <- read.csv("output_csvs/h_graded_results_finke.csv")
human_data_novel <- read.csv("output_csvs/h_graded_results_novel.csv")
```

```{r data_finke}
# Data
## Finke et al. Tasks
humans_finke_score <- sum(human_data_finke$overall_score)
humans_finke_max_score <- sum(human_data_finke$n_total) * 5

o3_finke_score <- llm_data_finke[llm_data_finke$Model == "OpenAI o3 Single Context (2025-07-21)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o3 Multiple Context (2025-07-21)", "overall_score"]
o3_finke_max_score <- (llm_data_finke[llm_data_finke$Model == "OpenAI o3 Single Context (2025-07-21)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o3 Multiple Context (2025-07-21)", "n_total"]) * 5

o3_images_finke_score <- llm_data_finke[llm_data_finke$Model == "OpenAI o3 Multiple Context w/ Images (2025-07-14)", "overall_score"]
o3_images_finke_max_score <- llm_data_finke[llm_data_finke$Model == "OpenAI o3 Multiple Context w/ Images (2025-07-14)", "n_total"] * 5

o3_pro_finke_score <- llm_data_finke[llm_data_finke$Model == "OpenAI o3 Pro Single Context (2025-07-21)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o3 Pro Multiple Context (2025-07-21)", "overall_score"]
o3_pro_finke_max_score <- (llm_data_finke[llm_data_finke$Model == "OpenAI o3 Pro Single Context (2025-07-21)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o3 Pro Multiple Context (2025-07-21)", "n_total"]) * 5

o4_mini_finke_score <- llm_data_finke[llm_data_finke$Model == "OpenAI o4-mini Multiple Context (2025-07-14)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o4-mini Single Context (2025-07-14)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o4-mini Multiple Context (2025-07-21)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o4-mini Single Context (2025-07-21)", "overall_score"]
o4_mini_finke_max_score <- (llm_data_finke[llm_data_finke$Model == "OpenAI o4-mini Multiple Context (2025-07-14)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o4-mini Single Context (2025-07-14)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o4-mini Multiple Context (2025-07-21)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI o4-mini Single Context (2025-07-21)", "n_total"]) * 5

chatgpt_4o_finke_score <- llm_data_finke[llm_data_finke$Model == "OpenAI ChatGPT-4o Single Context (2025-07-25)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI ChatGPT-4o Multiple Context (2025-07-25)", "overall_score"]
chatgpt_4o_finke_max_score <- (llm_data_finke[llm_data_finke$Model == "OpenAI ChatGPT-4o Single Context (2025-07-25)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "OpenAI ChatGPT-4o Multiple Context (2025-07-25)", "n_total"]) * 5

gpt4_1_finke_score <- llm_data_finke[llm_data_finke$Model == "GPT 4.1 Single Context (2025-07-21)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "GPT 4.1 Multiple Context (2025-07-21)", "overall_score"]
gpt4_1_finke_max_score <- (llm_data_finke[llm_data_finke$Model == "GPT 4.1 Single Context (2025-07-21)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "GPT 4.1 Multiple Context (2025-07-21)", "n_total"]) * 5

gpt4_1_images_finke_score <- llm_data_finke[llm_data_finke$Model == "GPT 4.1 Multiple Context w/ Images (2025-07-21)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "GPT 4.1 Single Context w/ Images (2025-07-21)", "overall_score"]
gpt4_1_images_finke_max_score <- (llm_data_finke[llm_data_finke$Model == "GPT 4.1 Multiple Context w/ Images (2025-07-21)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "GPT 4.1 Single Context w/ Images (2025-07-21)", "n_total"]) * 5

gemini2_5_finke_score <- llm_data_finke[llm_data_finke$Model == "Gemini 2.5 Pro Multiple Context (2025-07-21)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "Gemini 2.5 Pro Single Context (2025-07-21)", "overall_score"]
gemini2_5_finke_max_score <- (llm_data_finke[llm_data_finke$Model == "Gemini 2.5 Pro Multiple Context (2025-07-21)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "Gemini 2.5 Pro Single Context (2025-07-21)", "n_total"]) * 5

gemini2_0_flash_finke_score <- llm_data_finke[llm_data_finke$Model == "Gemini 2.0 Flash Multiple Context (2025-07-21)", "overall_score"] +
  llm_data_finke[llm_data_finke$Model == "Gemini 2.0 Flash Single Context (2025-07-21)", "overall_score"]
gemini2_0_flash_finke_max_score <- (llm_data_finke[llm_data_finke$Model == "Gemini 2.0 Flash Multiple Context (2025-07-21)", "n_total"] +
  llm_data_finke[llm_data_finke$Model == "Gemini 2.0 Flash Single Context (2025-07-21)", "n_total"]) * 5

gemini2_0_flash_images_finke_score <- llm_data_finke[llm_data_finke$Model == "Gemini 2.0 Flash Image Generation Multiple Context (2025-07-25)", "overall_score"]
gemini2_0_flash_images_finke_max_score <- llm_data_finke[llm_data_finke$Model == "Gemini 2.0 Flash Image Generation Multiple Context (2025-07-25)", "n_total"] * 5
```

```{r data_novel}
## Novel 48 Tasks
humans_novel_score <- sum(human_data_novel$overall_score)
humans_novel_max_score <- sum(human_data_novel$n_total) * 5

o3_novel_score <- llm_data_novel[llm_data_novel$Model == "OpenAI o3 Single Context (2025-07-21)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o3 Multiple Context (2025-07-21)", "overall_score"]
o3_novel_max_score <- (llm_data_novel[llm_data_novel$Model == "OpenAI o3 Single Context (2025-07-21)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o3 Multiple Context (2025-07-21)", "n_total"]) * 5

o3_images_novel_score <- llm_data_novel[llm_data_novel$Model == "OpenAI o3 Multiple Context w/ Images (2025-07-14)", "overall_score"]
o3_images_novel_max_score <- llm_data_novel[llm_data_novel$Model == "OpenAI o3 Multiple Context w/ Images (2025-07-14)", "n_total"] * 5

o3_pro_novel_score <- llm_data_novel[llm_data_novel$Model == "OpenAI o3 Pro Single Context (2025-07-21)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o3 Pro Multiple Context (2025-07-21)", "overall_score"]
o3_pro_novel_max_score <- (llm_data_novel[llm_data_novel$Model == "OpenAI o3 Pro Single Context (2025-07-21)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o3 Pro Multiple Context (2025-07-21)", "n_total"]) * 5

o4_mini_novel_score <- llm_data_novel[llm_data_novel$Model == "OpenAI o4-mini Multiple Context (2025-07-14)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o4-mini Single Context (2025-07-14)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o4-mini Multiple Context (2025-07-21)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o4-mini Single Context (2025-07-21)", "overall_score"]
o4_mini_novel_max_score <- (llm_data_novel[llm_data_novel$Model == "OpenAI o4-mini Multiple Context (2025-07-14)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o4-mini Single Context (2025-07-14)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o4-mini Multiple Context (2025-07-21)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI o4-mini Single Context (2025-07-21)", "n_total"]) * 5

chatgpt_4o_novel_score <- llm_data_novel[llm_data_novel$Model == "OpenAI ChatGPT-4o Single Context (2025-07-25)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI ChatGPT-4o Multiple Context (2025-07-25)", "overall_score"]
chatgpt_4o_novel_max_score <- (llm_data_novel[llm_data_novel$Model == "OpenAI ChatGPT-4o Single Context (2025-07-25)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "OpenAI ChatGPT-4o Multiple Context (2025-07-25)", "n_total"]) * 5

gpt4_1_novel_score <- llm_data_novel[llm_data_novel$Model == "GPT 4.1 Single Context (2025-07-21)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "GPT 4.1 Multiple Context (2025-07-21)", "overall_score"]
gpt4_1_novel_max_score <- (llm_data_novel[llm_data_novel$Model == "GPT 4.1 Single Context (2025-07-21)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "GPT 4.1 Multiple Context (2025-07-21)", "n_total"]) * 5

gpt4_1_images_novel_score <- llm_data_novel[llm_data_novel$Model == "GPT 4.1 Multiple Context w/ Images (2025-07-21)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "GPT 4.1 Single Context w/ Images (2025-07-21)", "overall_score"]
gpt4_1_images_novel_max_score <- (llm_data_novel[llm_data_novel$Model == "GPT 4.1 Multiple Context w/ Images (2025-07-21)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "GPT 4.1 Single Context w/ Images (2025-07-21)", "n_total"]) * 5

gemini2_5_novel_score <- llm_data_novel[llm_data_novel$Model == "Gemini 2.5 Pro Multiple Context (2025-07-21)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "Gemini 2.5 Pro Single Context (2025-07-21)", "overall_score"]
gemini2_5_novel_max_score <- (llm_data_novel[llm_data_novel$Model == "Gemini 2.5 Pro Multiple Context (2025-07-21)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "Gemini 2.5 Pro Single Context (2025-07-21)", "n_total"]) * 5

gemini2_0_flash_novel_score <- llm_data_novel[llm_data_novel$Model == "Gemini 2.0 Flash Multiple Context (2025-07-21)", "overall_score"] +
  llm_data_novel[llm_data_novel$Model == "Gemini 2.0 Flash Single Context (2025-07-21)", "overall_score"]
gemini2_0_flash_novel_max_score <- (llm_data_novel[llm_data_novel$Model == "Gemini 2.0 Flash Multiple Context (2025-07-21)", "n_total"] +
  llm_data_novel[llm_data_novel$Model == "Gemini 2.0 Flash Single Context (2025-07-21)", "n_total"]) * 5

gemini2_0_flash_images_novel_score <- llm_data_novel[llm_data_novel$Model == "Gemini 2.0 Flash Image Generation Multiple Context (2025-07-25)", "overall_score"]
gemini2_0_flash_images_novel_max_score <- llm_data_novel[llm_data_novel$Model == "Gemini 2.0 Flash Image Generation Multiple Context (2025-07-25)", "n_total"] * 5
```
```{r collapse_families}
## Collapse Families
o3_family_finke_score <- o3_finke_score +
  o3_images_finke_score +
  o3_pro_finke_score
o3_family_finke_max_score <- o3_finke_max_score +
  o3_images_finke_max_score +
  o3_pro_finke_max_score

o3_family_novel_score <- o3_novel_score +
  o3_images_novel_score +
  o3_pro_novel_score
o3_family_novel_max_score <- o3_novel_max_score +
  o3_images_novel_max_score +
  o3_pro_novel_max_score


o3_family_no_images_finke_score <- o3_finke_score + o3_pro_finke_score
o3_family_no_images_finke_max_score <- o3_finke_max_score + o3_pro_finke_max_score

o3_family_no_images_novel_score <- o3_novel_score + o3_pro_novel_score
o3_family_no_images_novel_max_score <- o3_novel_max_score + o3_pro_novel_max_score


gemini_family_finke_score <- gemini2_5_finke_score +
  gemini2_0_flash_finke_score +
  gemini2_0_flash_images_finke_score
gemini_family_finke_max_score <- gemini2_5_finke_max_score +
  gemini2_0_flash_finke_max_score +
  gemini2_0_flash_images_finke_max_score

gemini_family_novel_score <- gemini2_5_novel_score +
  gemini2_0_flash_novel_score +
  gemini2_0_flash_images_novel_score
gemini_family_novel_max_score <- gemini2_5_novel_max_score +
  gemini2_0_flash_novel_max_score +
  gemini2_0_flash_images_novel_max_score

openai_family_finke_score <- o3_family_finke_score +
  o4_mini_finke_score +
  chatgpt_4o_finke_score +
  gpt4_1_finke_score +
  gpt4_1_images_finke_score
openai_family_finke_max_score <- o3_family_finke_max_score +
  o4_mini_finke_max_score +
  chatgpt_4o_finke_max_score +
  gpt4_1_finke_max_score +
  gpt4_1_images_finke_max_score

openai_family_novel_score <- o3_family_novel_score +
  o4_mini_novel_score +
  chatgpt_4o_novel_score +
  gpt4_1_novel_score +
  gpt4_1_images_novel_score
openai_family_novel_max_score <- o3_family_novel_max_score +
  o4_mini_novel_max_score +
  chatgpt_4o_novel_max_score +
  gpt4_1_novel_max_score +
  gpt4_1_images_novel_max_score

openai_non_o3_family_finke_score <- o4_mini_finke_score +
  chatgpt_4o_finke_score +
  gpt4_1_finke_score +
  gpt4_1_images_finke_score
openai_non_o3_family_finke_max_score <- o4_mini_finke_max_score +
  chatgpt_4o_finke_max_score +
  gpt4_1_finke_max_score +
  gpt4_1_images_finke_max_score

openai_non_o3_family_novel_score <- o4_mini_novel_score +
  chatgpt_4o_novel_score +
  gpt4_1_novel_score +
  gpt4_1_images_novel_score
openai_non_o3_family_novel_max_score <- o4_mini_novel_max_score +
  chatgpt_4o_novel_max_score +
  gpt4_1_novel_max_score +
  gpt4_1_images_novel_max_score
```

```{r collapse_total}
## Collapsed Data (Finke + 48 Novel)
humans_total_score <- humans_finke_score + humans_novel_score
humans_total_max_score <- humans_finke_max_score + humans_novel_max_score

o3_total_score <- o3_finke_score + o3_novel_score
o3_total_max_score <- o3_finke_max_score + o3_novel_max_score

o3_images_total_score <- o3_images_finke_score + o3_images_novel_score
o3_images_total_max_score <- o3_images_finke_max_score + o3_images_novel_max_score

o3_pro_total_score <- o3_pro_finke_score + o3_pro_novel_score
o3_pro_total_max_score <- o3_pro_finke_max_score + o3_pro_novel_max_score

o4_mini_total_score <- o4_mini_finke_score + o4_mini_novel_score
o4_mini_total_max_score <- o4_mini_finke_max_score + o4_mini_novel_max_score

chatgpt_4o_total_score <- chatgpt_4o_finke_score + chatgpt_4o_novel_score
chatgpt_4o_total_max_score <- chatgpt_4o_finke_max_score + chatgpt_4o_novel_max_score

gpt4_1_total_score <- gpt4_1_finke_score + gpt4_1_novel_score
gpt4_1_total_max_score <- gpt4_1_finke_max_score + gpt4_1_novel_max_score

gpt4_1_images_total_score <- gpt4_1_images_finke_score + gpt4_1_images_novel_score
gpt4_1_images_total_max_score <- gpt4_1_images_finke_max_score + gpt4_1_images_novel_max_score

gemini2_5_total_score <- gemini2_5_finke_score + gemini2_5_novel_score
gemini2_5_total_max_score <- gemini2_5_finke_max_score + gemini2_5_novel_max_score

gemini2_0_flash_total_score <- gemini2_0_flash_finke_score + gemini2_0_flash_novel_score
gemini2_0_flash_total_max_score <- gemini2_0_flash_finke_max_score + gemini2_0_flash_novel_max_score

gemini2_0_flash_images_total_score <- gemini2_0_flash_images_finke_score + gemini2_0_flash_images_novel_score
gemini2_0_flash_images_total_max_score <- gemini2_0_flash_images_finke_max_score + gemini2_0_flash_images_novel_max_score

o3_family_total_score <- o3_family_finke_score + o3_family_novel_score
o3_family_total_max_score <- o3_family_finke_max_score + o3_family_novel_max_score

o3_family_no_images_total_score <- o3_family_no_images_finke_score + o3_family_no_images_novel_score
o3_family_no_images_total_max_score <- o3_family_no_images_finke_max_score + o3_family_no_images_novel_max_score

all_gemini_total_score <- gemini_family_finke_score + gemini_family_novel_score
all_gemini_total_max_score <- gemini_family_finke_max_score + gemini_family_novel_max_score

all_openAI_total_score <- openai_family_finke_score + openai_family_novel_score
all_openAI_total_max_score <- openai_family_finke_max_score + openai_family_novel_max_score

other_openAI_total_score <- openai_non_o3_family_finke_score + openai_non_o3_family_novel_score
other_openAI_total_max_score <- openai_non_o3_family_finke_max_score + openai_non_o3_family_novel_max_score

## Original Finke Data - modified towards the new scoring system
original_finke_exp2_correct <- 37 * 5 + 72 - 37
original_finke_exp2_total <- 72 * 5

original_finke_exp3_correct <- 28 * 5 + 72 - 28
original_finke_exp3_total <- 72 * 5

# Collapsed Original Finke (Exp 2 + Exp 3)
original_finke_correct <- original_finke_exp2_correct + original_finke_exp3_correct
original_finke_total <- original_finke_exp2_total + original_finke_exp3_total
```
```{r finke_dataframe}
# Create data frames for easier manipulation
finke_data <- data.frame(
  model = c("Humans", "o3", "o3-GPT-Image",
            "o3-Pro", "GPT-4.1", "GPT-4.1-GPT-Image",
            "ChatGPT-4o", "o4-mini", "Gemini-2.5",
            "Gemini-2.0-Flash", "Gemini-2.0-Flash-GPT-Image",
            "All-OpenAI", "Other-OpenAI", "All-Gemini"),
  correct = c(humans_finke_score, o3_finke_score, o3_images_finke_score,
              o3_pro_finke_score, gpt4_1_finke_score, gpt4_1_images_finke_score,
              chatgpt_4o_finke_score, o4_mini_finke_score, gemini2_5_finke_score,
              gemini2_0_flash_finke_score, gemini2_0_flash_images_finke_score,
              openai_family_finke_score, openai_non_o3_family_finke_score, gemini_family_finke_score),
  total = c(humans_finke_max_score, o3_finke_max_score, o3_images_finke_max_score,
            o3_pro_finke_max_score, gpt4_1_finke_max_score, gpt4_1_images_finke_max_score,
            chatgpt_4o_finke_max_score, o4_mini_finke_max_score, gemini2_5_finke_max_score,
            gemini2_0_flash_finke_max_score, gemini2_0_flash_images_finke_max_score,
            openai_family_finke_max_score, openai_non_o3_family_finke_max_score, gemini_family_finke_max_score)
)

# Calculate proportions from correct/total
finke_data$proportion <- finke_data$correct / finke_data$total
```
```{r novel_dataframe}
novel_data <- data.frame(
  model = c("Humans", "o3", "o3-GPT-Image",
            "o3-Pro", "GPT-4.1", "GPT-4.1-GPT-Image",
            "ChatGPT-4o", "o4-mini", "Gemini-2.5",
            "Gemini-2.0-Flash", "Gemini-2.0-Flash-GPT-Image",
            "All-OpenAI", "Other-OpenAI", "All-Gemini"),
    correct = c(humans_novel_score, o3_novel_score, o3_images_novel_score,
                o3_pro_novel_score, gpt4_1_novel_score, gpt4_1_images_novel_score,
                chatgpt_4o_novel_score, o4_mini_novel_score, gemini2_5_novel_score,
                gemini2_0_flash_novel_score, gemini2_0_flash_images_novel_score,
                openai_family_novel_score, openai_non_o3_family_novel_score, gemini_family_novel_score),
    total = c(humans_novel_max_score, o3_novel_max_score, o3_images_novel_max_score,
                o3_pro_novel_max_score, gpt4_1_novel_max_score, gpt4_1_images_novel_max_score,
                chatgpt_4o_novel_max_score, o4_mini_novel_max_score, gemini2_5_novel_max_score,
                gemini2_0_flash_novel_max_score, gemini2_0_flash_images_novel_max_score,
                openai_family_novel_max_score, openai_non_o3_family_novel_max_score, gemini_family_novel_max_score)
)

# Calculate proportions from correct/total
novel_data$proportion <- novel_data$correct / novel_data$total

```

```{r collapsed_dataframe}

collapsed_data <- data.frame(
    model = c("Humans", "o3", "o3-GPT-Image",
                "o3-Pro", "GPT-4.1", "GPT-4.1-GPT-Image",
                "ChatGPT-4o", "o4-mini", "Gemini-2.5",
                "Gemini-2.0-Flash", "Gemini-2.0-Flash-GPT-Image",
                "All-OpenAI", "Other-OpenAI", "All-Gemini"),
    correct = c(humans_total_score, o3_total_score, o3_images_total_score,
                o3_pro_total_score, gpt4_1_total_score, gpt4_1_images_total_score,
                chatgpt_4o_total_score, o4_mini_total_score, gemini2_5_total_score,
                gemini2_0_flash_total_score, gemini2_0_flash_images_total_score,
                all_openAI_total_score, other_openAI_total_score, all_gemini_total_score),
    total = c(humans_total_max_score, o3_total_max_score, o3_images_total_max_score,
                o3_pro_total_max_score, gpt4_1_total_max_score, gpt4_1_images_total_max_score,
                chatgpt_4o_total_max_score, o4_mini_total_max_score, gemini2_5_total_max_score,
                gemini2_0_flash_total_max_score, gemini2_0_flash_images_total_max_score,
                all_openAI_total_max_score, other_openAI_total_max_score, all_gemini_total_max_score)
    )



# Calculate proportions from correct/total
collapsed_data$proportion <- collapsed_data$correct / collapsed_data$total
```

```{r dislay_data}
# Display the data
cat("Finke et al. Tasks Data:\n")
print(finke_data)
cat("\n48 Novel Tasks Data:\n")
print(novel_data)
cat("\nCollapsed Data (Finke + 48 Novel Tasks):\n")
print(collapsed_data)

# Display Original Finke data
cat("\n\nOriginal Finke Data:\n")
cat("Exp 2: ", original_finke_exp2_correct, "/", original_finke_exp2_total,
    " (", round(original_finke_exp2_correct / original_finke_exp2_total, 3), ")\n", sep = "")
cat("Exp 3: ", original_finke_exp3_correct, "/", original_finke_exp3_total,
    " (", round(original_finke_exp3_correct / original_finke_exp3_total, 3), ")\n", sep = "")
cat("Collapsed Original Finke: ", original_finke_correct, "/", original_finke_total,
    " (", round(original_finke_correct / original_finke_total, 3), ")\n", sep = "")
```

## Proportion Testing Function

```{r functions}
# Function to perform proportion test and extract results
perform_prop_test <- function(model1_name, model1_correct, model1_total,
                              model2_name, model2_correct, model2_total) {

  # Perform the test
  test_result <- prop.test(x = c(model1_correct, model2_correct),
                           n = c(model1_total, model2_total),
                           alternative = "two.sided",
                           conf.level = 0.95,
                           correct = TRUE)

  # Calculate proportions
  prop1 <- model1_correct / model1_total
  prop2 <- model2_correct / model2_total
  diff <- prop1 - prop2

  # Return results as a list
  return(list(
    comparison = paste(model1_name, "vs", model2_name),
    model1 = model1_name,
    model2 = model2_name,
    prop1 = prop1,
    prop2 = prop2,
    diff = diff,
    chi_squared = test_result$statistic,
    df = test_result$parameter,
    p_value = test_result$p.value,
    ci_lower = test_result$conf.int[1],
    ci_upper = test_result$conf.int[2],
    significant = test_result$p.value < 0.05
  ))
}

# Function to test all combinations
test_all_combinations <- function(data, task_name) {
  results <- list()
  counter <- 1

  # Test all unique pairs
  for (i in 1:(nrow(data) - 1)) {
    for (j in (i + 1):nrow(data)) {
      results[[counter]] <- perform_prop_test(
        data$model[i], data$correct[i], data$total[i],
        data$model[j], data$correct[j], data$total[j]
      )
      counter <- counter + 1
    }
  }

  # Convert to data frame
  results_df <- do.call(rbind, lapply(results, as.data.frame))
  results_df$task <- task_name

  return(results_df)
}
```

## Comparison: o3 Family Single Context vs Multiple Context

```{r o3_single_vs_multiple, echo = FALSE}
# Perform proportion test between o3 single context and multiple context
o3_single_vs_multiple <- prop.test(x = c(o3_finke_score, o3_images_finke_score),
                                  n = c(o3_finke_max_score, o3_images_finke_max_score),
                                  alternative = "two.sided",
                                  conf.level = 0.95,
                                  correct = TRUE)
# Display results
cat("\n\nComparison: o3 Family Single Context vs Multiple Context (Finke Tasks)\n")
cat(paste(rep("=", 70), collapse = ""), "\n")
cat("o3 Single Context: ", o3_finke_score, "/", o3_finke_max_score,
    " (", round(o3_finke_score / o3_finke_max_score, 3), ")\n", sep = "")
cat("o3 Multiple Context: ", o3_images_finke_score, "/", o3_images_finke_max_score,
    " (", round(o3_images_finke_score / o3_images_finke_max_score, 3), ")\n", sep = "")
cat("Difference: ", round(o3_finke_score / o3_finke_max_score - o3_images_finke_score / o3_images_finke_max_score, 3), "\n")
cat("Chi-squared: ", round(o3_single_vs_multiple$statistic, 3), "\n")
cat("P-value: ", format(o3_single_vs_multiple$p.value, scientific = FALSE, digits = 4), "\n")
cat("95% CI: [", round(o3_single_vs_multiple$conf.int[1], 3), ", ",
    round(o3_single_vs_multiple$conf.int[2], 3), "]\n")
cat("Significant: ", ifelse(o3_single_vs_multiple$p.value < 0.05, "YES (p < 0.05)", "NO"), "\n")
# Create a formatted summary similar to other comparisons
cat("\n\nDetailed Comparison: o3 Single Context vs Multiple Context\n")
cat(paste(rep("-", 40), collapse = ""), "\n")
cat("Proportions: ", round(o3_finke_score / o3_finke_max_score, 3), " vs ",
    round(o3_images_finke_score / o3_images_finke_max_score, 3), "\n")
cat("Difference: ", round(o3_finke_score / o3_finke_max_score - o3_images_finke_score / o3_images_finke_max_score, 3), "\n")
cat("Chi-squared: ", round(o3_single_vs_multiple$statistic, 3), "\n")
cat("Degrees of freedom: ", o3_single_vs_multiple$parameter, "\n")
cat("P-value: ", format(o3_single_vs_multiple$p.value, scientific = FALSE, digits = 4), "\n")
cat("95% CI: [", round(o3_single_vs_multiple$conf.int[1], 3), ", ",
    round(o3_single_vs_multiple$conf.int[2], 3), "]\n")
cat("Significant: ", ifelse(o3_single_vs_multiple$p.value < 0.05, "YES (p < 0.05)", "NO"), "\n")
# Create summary table
o3_single_vs_multiple_summary <- data.frame(
  comparison = "o3 Single Context vs Multiple Context",
  diff = round(o3_finke_score / o3_finke_max_score - o3_images_finke_score / o3_images_finke_max_score, 3),
  p_value = round(o3_single_vs_multiple$p.value, 4),
  significant = o3_single_vs_multiple$p.value < 0.05
)
cat("\n\nSummary Table - o3 Single vs Multiple Context:\n")
print(kable(o3_single_vs_multiple_summary, format = "simple"))
```

## Comparison: Current Human Finke vs Original Finke

```{r human_vs_original_finke, echo = FALSE}
# Perform proportion test between current human Finke performance and original Finke data
human_vs_original <- prop.test(x = c(humans_finke_score, original_finke_correct),
                               n = c(humans_finke_max_score, original_finke_total),
                               alternative = "two.sided",
                               conf.level = 0.95,
                               correct = TRUE)

# Display results
cat("\n\nComparison: Current Human Finke vs Original Finke (Collapsed Exp 2 + Exp 3)\n")
cat(paste(rep("=", 70), collapse = ""), "\n")
cat("Current Human Finke: ", humans_finke_score, "/", humans_finke_max_score,
    " (", round(humans_finke_score / humans_finke_max_score, 3), ")\n", sep = "")
cat("Original Finke: ", original_finke_correct, "/", original_finke_total,
    " (", round(original_finke_correct / original_finke_total, 3), ")\n", sep = "")
cat("Difference: ", round(humans_finke_score / humans_finke_max_score - original_finke_correct / original_finke_total, 3), "\n")
cat("Chi-squared: ", round(human_vs_original$statistic, 3), "\n")
cat("P-value: ", format(human_vs_original$p.value, scientific = FALSE, digits = 4), "\n")
cat("95% CI: [", round(human_vs_original$conf.int[1], 3), ", ",
    round(human_vs_original$conf.int[2], 3), "]\n")
cat("Significant: ", ifelse(human_vs_original$p.value < 0.05, "YES (p < 0.05)", "NO"), "\n")

# Create a formatted summary similar to other comparisons
cat("\n\nDetailed Comparison: Current Humans vs Original Finke\n")
cat(paste(rep("-", 40), collapse = ""), "\n")
cat("Proportions: ", round(humans_finke_score / humans_finke_max_score, 3), " vs ",
    round(original_finke_correct / original_finke_total, 3), "\n")
cat("Difference: ", round(humans_finke_score / humans_finke_max_score - original_finke_correct / original_finke_total, 3), "\n")
cat("Chi-squared: ", round(human_vs_original$statistic, 3), "\n")
cat("Degrees of freedom: ", human_vs_original$parameter, "\n")
cat("P-value: ", format(human_vs_original$p.value, scientific = FALSE, digits = 4), "\n")
cat("95% CI: [", round(human_vs_original$conf.int[1], 3), ", ",
    round(human_vs_original$conf.int[2], 3), "]\n")
cat("Significant: ", ifelse(human_vs_original$p.value < 0.05, "YES (p < 0.05)", "NO"), "\n")

# Create summary table
human_vs_original_summary <- data.frame(
  comparison = "Current Humans vs Original Finke",
  diff = round(humans_finke_score / humans_finke_max_score - original_finke_correct / original_finke_total, 3),
  p_value = round(human_vs_original$p.value, 4),
  significant = human_vs_original$p.value < 0.05
)

cat("\n\nSummary Table - Human vs Original Finke:\n")
print(kable(human_vs_original_summary, format = "simple"))
```

## Comparison: Current Human 48 vs Original Finke

```{r human_48_vs_original_finke, echo = FALSE}
# Perform proportion test between current human 48 performance and original Finke data
human_48_vs_original <- prop.test(x = c(humans_novel_score, original_finke_correct),
                                  n = c(humans_novel_max_score, original_finke_total),
                                  alternative = "two.sided",
                                  conf.level = 0.95,
                                  correct = TRUE)

# Display results
cat("\n\nComparison: Current Human 48-Item Task vs Original Finke (Collapsed Exp 2 + Exp 3)\n")
cat(paste(rep("=", 70), collapse = ""), "\n")
cat("Current Human 48: ", humans_novel_score, "/", humans_novel_max_score,
    " (", round(humans_novel_score / humans_novel_max_score, 3), ")\n", sep = "")
cat("Original Finke: ", original_finke_correct, "/", original_finke_total,
    " (", round(original_finke_correct / original_finke_total, 3), ")\n", sep = "")
cat("Difference: ", round(humans_novel_score / humans_novel_max_score - original_finke_correct / original_finke_total, 3), "\n")
cat("Chi-squared: ", round(human_48_vs_original$statistic, 3), "\n")
cat("P-value: ", format(human_48_vs_original$p.value, scientific = FALSE, digits = 4), "\n")
cat("95% CI: [", round(human_48_vs_original$conf.int[1], 3), ", ",
    round(human_48_vs_original$conf.int[2], 3), "]\n")
cat("Significant: ", ifelse(human_48_vs_original$p.value < 0.05, "YES (p < 0.05)", "NO"), "\n")

# Create a formatted summary similar to other comparisons
cat("\n\nDetailed Comparison: Current Humans vs Original Finke\n")
cat(paste(rep("-", 40), collapse = ""), "\n")
cat("Proportions: ", round(humans_novel_score / humans_novel_max_score, 3), " vs ",
    round(original_finke_correct / original_finke_total, 3), "\n")
cat("Difference: ", round(humans_novel_score / humans_novel_max_score - original_finke_correct / original_finke_total, 3), "\n")
cat("Chi-squared: ", round(human_48_vs_original$statistic, 3), "\n")
cat("Degrees of freedom: ", human_48_vs_original$parameter, "\n")
cat("P-value: ", format(human_48_vs_original$p.value, scientific = FALSE, digits = 4), "\n")
cat("95% CI: [", round(human_48_vs_original$conf.int[1], 3), ", ",
    round(human_48_vs_original$conf.int[2], 3), "]\n")
cat("Significant: ", ifelse(human_48_vs_original$p.value < 0.05, "YES (p < 0.05)", "NO"), "\n")

# Create summary table
human_48_vs_original_summary <- data.frame(
  comparison = "Current Humans vs Original Finke",
  diff = round(humans_novel_score / humans_novel_max_score - original_finke_correct / original_finke_total, 3),
  p_value = round(human_48_vs_original$p.value, 4),
  significant = human_48_vs_original$p.value < 0.05
)

cat("\n\nSummary Table - Human vs Original Finke:\n")
print(kable(human_48_vs_original_summary, format = "simple"))
```
## Comparison: Current Humans (collapsed) vs Original Finke

```{r human_collapsed_vs_original_finke, echo = FALSE}
# Perform proportion test between current human 48 performance and original Finke data
human_vs_original_collapsed <- prop.test(x = c(collapsed_data$correct[1], original_finke_correct),
                                         n = c(collapsed_data$total[1], original_finke_total),
                                         alternative = "two.sided",
                                         conf.level = 0.95,
                                         correct = TRUE)

# Display results
cat("\n\nComparison: Current Human 48-Item Task vs Original Finke (Collapsed Exp 2 + Exp 3)\n")
cat(paste(rep("=", 70), collapse = ""), "\n")
cat("Current Human Finke: ", collapsed_data$correct[1], "/", collapsed_data$total[1],
    " (", round(collapsed_data$correct[1] / collapsed_data$total[1], 3), ")\n", sep = "")
cat("Original Finke: ", original_finke_correct, "/", original_finke_total,
    " (", round(original_finke_correct / original_finke_total, 3), ")\n", sep = "")
cat("Difference: ", round(collapsed_data$correct[1] / collapsed_data$total[1] - original_finke_correct / original_finke_total, 3), "\n")
cat("Chi-squared: ", round(human_vs_original_collapsed$statistic, 3), "\n")
cat("P-value: ", format(human_vs_original_collapsed$p.value, scientific = FALSE, digits = 4), "\n")
cat("95% CI: [", round(human_vs_original_collapsed$conf.int[1], 3), ", ",
    round(human_vs_original_collapsed$conf.int[2], 3), "]\n")
cat("Significant: ", ifelse(human_vs_original_collapsed$p.value < 0.05, "YES (p < 0.05)", "NO"), "\n")

# Create a formatted summary similar to other comparisons
cat("\n\nDetailed Comparison: Current Humans vs Original Finke\n")
cat(paste(rep("-", 40), collapse = ""), "\n")
cat("Proportions: ", round(collapsed_data$correct[1] / collapsed_data$total[1], 3), " vs ",
    round(original_finke_correct / original_finke_total, 3), "\n")
cat("Difference: ", round(collapsed_data$correct[1] / collapsed_data$total[1] - original_finke_correct / original_finke_total, 3), "\n")
cat("Chi-squared: ", round(human_vs_original_collapsed$statistic, 3), "\n")
cat("Degrees of freedom: ", human_vs_original_collapsed$parameter, "\n")
cat("P-value: ", format(human_vs_original_collapsed$p.value, scientific = FALSE, digits = 4), "\n")
cat("95% CI: [", round(human_vs_original_collapsed$conf.int[1], 3), ", ",
    round(human_vs_original_collapsed$conf.int[2], 3), "]\n")
cat("Significant: ", ifelse(human_vs_original_collapsed$p.value < 0.05, "YES (p < 0.05)", "NO"), "\n")

# Create summary table
human_vs_original_collapsed_summary <- data.frame(
  comparison = "Current Humans (collapsed) vs Original Finke",
  diff = round(collapsed_data$correct[1] / collapsed_data$total[1] - original_finke_correct / original_finke_total, 3),
  p_value = round(human_vs_original_collapsed$p.value, 4),
  significant = human_vs_original_collapsed$p.value < 0.05
)

cat("\n\nSummary Table - Current Human (Collapsed) vs Original Finke:\n")
print(kable(human_vs_original_collapsed_summary, format = "simple"))
```
## Finke et al. Tasks - All Pairwise Comparisons

```{r finke_comparisons}
# Test all combinations for Finke tasks
finke_results <- test_all_combinations(finke_data, "Finke")

# Display results
cat("All Pairwise Comparisons for Finke et al. Tasks:\n")
cat(paste(rep("=", 80), collapse = ""), "\n")

for (i in 1:nrow(finke_results)) {
  cat("\n", finke_results$comparison[i], "\n")
  cat(paste(rep("-", 40), collapse = ""), "\n")
  cat("Proportions: ", round(finke_results$prop1[i], 3), " vs ",
      round(finke_results$prop2[i], 3), "\n")
  cat("Difference: ", round(finke_results$diff[i], 3), "\n")
  cat("Chi-squared: ", round(finke_results$chi_squared[i], 3), "\n")
  cat("Degrees of freedom: ", round(finke_results$df[i], 3), "\n")
  cat("P-value: ", format(finke_results$p_value[i], scientific = FALSE, digits = 4), "\n")
  cat("95% CI: [", round(finke_results$ci_lower[i], 3), ", ",
      round(finke_results$ci_upper[i], 3), "]\n")
  cat("Significant: ", ifelse(finke_results$significant[i], "YES (p < 0.05)", "NO"), "\n")
}

# Summary table
finke_summary <- finke_results %>%
  select(comparison, diff, chi_squared, p_value, significant) %>%
  mutate(diff = round(diff, 3),
         p_value = round(p_value, 4))

cat("\n\nSummary Table - Finke Tasks:\n")
print(kable(finke_summary, format = "simple"))
```

## 48 Novel Tasks - All Pairwise Comparisons

```{r novel_48_comparisons}
# Test all combinations for 48 Novel tasks
novel_48_results <- test_all_combinations(novel_data, "48 Novel")

# Display results
cat("All Pairwise Comparisons for 48 Novel Tasks:\n")
cat(paste(rep("=", 80), collapse = ""), "\n")

for (i in 1:nrow(novel_48_results)) {
  cat("\n", novel_48_results$comparison[i], "\n")
  cat(paste(rep("-", 40), collapse = ""), "\n")
  cat("Proportions: ", round(novel_48_results$prop1[i], 3), " vs ",
      round(novel_48_results$prop2[i], 3), "\n")
  cat("Difference: ", round(novel_48_results$diff[i], 3), "\n")
  cat("Chi-squared: ", round(novel_48_results$chi_squared[i], 3), "\n")
  cat("Degrees of freedom: ", round(novel_48_results$df[i], 3), "\n")
  cat("P-value: ", format(novel_48_results$p_value[i], scientific = FALSE, digits = 4), "\n")
  cat("95% CI: [", round(novel_48_results$ci_lower[i], 3), ", ",
      round(novel_48_results$ci_upper[i], 3), "]\n")
  cat("Significant: ", ifelse(novel_48_results$significant[i], "YES (p < 0.05)", "NO"), "\n")
}

# Summary table
novel_48_summary <- novel_48_results %>%
  select(comparison, diff, chi_squared, p_value, significant) %>%
  mutate(diff = round(diff, 3),
         p_value = round(p_value, 4))

cat("\n\nSummary Table - 48 Novel Tasks:\n")
print(kable(novel_48_summary, format = "simple"))
```

## Visualization of All Comparisons

```{r visualizations, fig.width=12, fig.height=8}

# Plot 1: Proportions with confidence intervals for Finke tasks
finke_plot <- ggplot(finke_data, aes(x = reorder(model, proportion), y = proportion)) +
  geom_point(size = 4, color = "darkblue") +
  geom_errorbar(aes(ymin = proportion - 1.96 * sqrt(proportion * (1 - proportion) / total),
                    ymax = proportion + 1.96 * sqrt(proportion * (1 - proportion) / total)),
                width = 0.2, size = 1, color = "darkblue") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Finke et al. Tasks - Proportions with 95% CI",
       x = "Model",
       y = "Proportion Correct") +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"))

# Plot 2: Proportions with confidence intervals for 48 Novel tasks
novel_48_plot <- ggplot(novel_data, aes(x = reorder(model, proportion), y = proportion)) +
  geom_point(size = 4, color = "darkgreen") +
  geom_errorbar(aes(ymin = proportion - 1.96 * sqrt(proportion * (1 - proportion) / total),
                    ymax = proportion + 1.96 * sqrt(proportion * (1 - proportion) / total)),
                width = 0.2, size = 1, color = "darkgreen") +
  coord_flip() +
  theme_minimal() +
  labs(title = "48 Novel Tasks - Proportions with 95% CI",
       x = "Model",
       y = "Proportion Correct") +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"))

# Combine plots
combined_plot <- finke_plot + novel_48_plot
print(combined_plot)
```

## Heatmap of P-values

```{r heatmap, fig.width=10, fig.height=10}
# Create matrix of p-values for Finke tasks
finke_models <- finke_data$model
finke_pval_matrix <- matrix(NA, nrow = length(finke_models), ncol = length(finke_models))
rownames(finke_pval_matrix) <- finke_models
colnames(finke_pval_matrix) <- finke_models

for (i in 1:nrow(finke_results)) {
  row_idx <- which(finke_models == finke_results$model1[i])
  col_idx <- which(finke_models == finke_results$model2[i])
  finke_pval_matrix[row_idx, col_idx] <- finke_results$p_value[i]
  finke_pval_matrix[col_idx, row_idx] <- finke_results$p_value[i]
}

# Set diagonal to NA
diag(finke_pval_matrix) <- NA

# Create matrix of p-values for 48 Novel tasks
novel_models <- novel_data$model
novel_pval_matrix <- matrix(NA, nrow = length(novel_models), ncol = length(novel_models))
rownames(novel_pval_matrix) <- novel_models
colnames(novel_pval_matrix) <- novel_models

for (i in 1:nrow(novel_48_results)) {
  row_idx <- which(novel_models == novel_48_results$model1[i])
  col_idx <- which(novel_models == novel_48_results$model2[i])
  novel_pval_matrix[row_idx, col_idx] <- novel_48_results$p_value[i]
  novel_pval_matrix[col_idx, row_idx] <- novel_48_results$p_value[i]
}

# Set diagonal to NA
diag(novel_pval_matrix) <- NA

# Plot heatmaps
par(mfrow = c(2, 1), mar = c(6, 6, 3, 2))  # Increase margins for labels

# Define color palette
col_palette <- colorRampPalette(c("lightcyan", "lightblue", "lightskyblue", "steelblue4"))(20)

# Finke heatmap
image(finke_pval_matrix, axes = FALSE, col = col_palette, main = "P-values Heatmap - Finke Tasks")
axis(1, at = seq(0, 1, length.out = length(finke_models)), labels = finke_models,
     las = 2, cex.axis = 0.8)  # las=2 makes labels perpendicular, cex.axis makes them smaller
axis(2, at = seq(0, 1, length.out = length(finke_models)), labels = finke_models,
     las = 2, cex.axis = 0.8)

# Add gray color for diagonal
for (i in 1:length(finke_models)) {
  x_pos <- (i - 1) / (length(finke_models) - 1)
  y_pos <- (i - 1) / (length(finke_models) - 1)
  rect(x_pos - 0.5 / (length(finke_models) - 1), y_pos - 0.5 / (length(finke_models) - 1),
       x_pos + 0.5 / (length(finke_models) - 1), y_pos + 0.5 / (length(finke_models) - 1),
       col = "gray80", border = NA)
}

# Add p-values to the plot
for (i in 1:nrow(finke_pval_matrix)) {
  for (j in 1:ncol(finke_pval_matrix)) {
    if (!is.na(finke_pval_matrix[i, j])) {
      x_pos <- (j - 1) / (ncol(finke_pval_matrix) - 1)
      y_pos <- (i - 1) / (nrow(finke_pval_matrix) - 1)
      text(x_pos, y_pos, sprintf("%.3f", finke_pval_matrix[i, j]), cex = 0.7)
    }
  }
}

# 48 Novel heatmap
image(novel_pval_matrix, axes = FALSE, col = col_palette, main = "P-values Heatmap - 48 Novel Tasks")
axis(1, at = seq(0, 1, length.out = length(novel_models)), labels = novel_models,
     las = 2, cex.axis = 0.8)  # las=2 makes labels perpendicular, cex.axis makes them smaller
axis(2, at = seq(0, 1, length.out = length(novel_models)), labels = novel_models,
     las = 2, cex.axis = 0.8)

# Add gray color for diagonal
for (i in 1:length(novel_models)) {
  x_pos <- (i - 1) / (length(novel_models) - 1)
  y_pos <- (i - 1) / (length(novel_models) - 1)
  rect(x_pos - 0.5 / (length(novel_models) - 1), y_pos - 0.5 / (length(novel_models) - 1),
       x_pos + 0.5 / (length(novel_models) - 1), y_pos + 0.5 / (length(novel_models) - 1),
       col = "gray80", border = NA)
}

# Add p-values to the plot
for (i in 1:nrow(novel_pval_matrix)) {
  for (j in 1:ncol(novel_pval_matrix)) {
    if (!is.na(novel_pval_matrix[i, j])) {
      x_pos <- (j - 1) / (ncol(novel_pval_matrix) - 1)
      y_pos <- (i - 1) / (nrow(novel_pval_matrix) - 1)
      text(x_pos, y_pos, sprintf("%.3f", novel_pval_matrix[i, j]), cex = 0.7)
    }
  }
}
```

## Summary of Significant Differences

```{r summary_significant}
# Count significant differences for each task
finke_sig_count <- sum(finke_results$significant)
novel_48_sig_count <- sum(novel_48_results$significant)

cat("Summary of Significant Differences:\n")
cat(paste(rep("=", 50), collapse = ""), "\n")
cat("Finke Tasks:\n")
cat("  Total comparisons:", nrow(finke_results), "\n")
cat("  Significant differences:", finke_sig_count, "\n")
cat("  Percentage significant:", round(finke_sig_count / nrow(finke_results) * 100, 1), "%\n\n")

cat("48 Novel Tasks:\n")
cat("  Total comparisons:", nrow(novel_48_results), "\n")
cat("  Significant differences:", novel_48_sig_count, "\n")
cat("  Percentage significant:", round(novel_48_sig_count / nrow(novel_48_results) * 100, 1), "%\n\n")

# Show which comparisons are significant
cat("Significant Comparisons in Finke Tasks:\n")
finke_sig <- finke_results[finke_results$significant, c("comparison", "diff", "p_value")]
if (nrow(finke_sig) > 0) {
  print(kable(finke_sig, format = "simple", digits = 4))
} else {
  cat("  None\n")
}

cat("\nSignificant Comparisons in 48 Novel Tasks:\n")
novel_sig <- novel_48_results[novel_48_results$significant, c("comparison", "diff", "p_value")]
if (nrow(novel_sig) > 0) {
  print(kable(novel_sig, format = "simple", digits = 4))
} else {
  cat("  None\n")
}
```

## Collapsed Analysis - Finke + 48 Novel Tasks Combined

```{r collapsed_comparisons}
# Test all combinations for collapsed data
collapsed_results <- test_all_combinations(collapsed_data, "Collapsed (Finke + 48 Novel)")

# Display results
cat("All Pairwise Comparisons for Collapsed Data (Finke + 48 Novel Tasks):\n")
cat(paste(rep("=", 80), collapse = ""), "\n")

for (i in 1:nrow(collapsed_results)) {
  cat("\n", collapsed_results$comparison[i], "\n")
  cat(paste(rep("-", 40), collapse = ""), "\n")
  cat("Proportions: ", round(collapsed_results$prop1[i], 3), " vs ",
      round(collapsed_results$prop2[i], 3), "\n")
  cat("Difference: ", round(collapsed_results$diff[i], 3), "\n")
  cat("Chi-squared: ", round(collapsed_results$chi_squared[i], 3), "\n")
  cat("Degrees of freedom: ", round(collapsed_results$df[i], 3), "\n")
  cat("P-value: ", format(collapsed_results$p_value[i], scientific = FALSE, digits = 4), "\n")
  cat("95% CI: [", round(collapsed_results$ci_lower[i], 3), ", ",
      round(collapsed_results$ci_upper[i], 3), "]\n")
  cat("Significant: ", ifelse(collapsed_results$significant[i], "YES (p < 0.05)", "NO"), "\n")
}

# Summary table
collapsed_summary <- collapsed_results %>%
  select(comparison, diff, chi_squared, p_value, significant) %>%
  mutate(diff = round(diff, 3),
         p_value = round(p_value, 4))

cat("\n\nSummary Table - Collapsed Data:\n")
print(kable(collapsed_summary, format = "simple"))

# Count significant differences
collapsed_sig_count <- sum(collapsed_results$significant)

cat("\n\nCollapsed Data Summary:\n")
cat("  Total comparisons:", nrow(collapsed_results), "\n")
cat("  Significant differences:", collapsed_sig_count, "\n")
cat("  Percentage significant:", round(collapsed_sig_count / nrow(collapsed_results) * 100, 1), "%\n\n")

# Show significant comparisons
cat("Significant Comparisons in Collapsed Data:\n")
collapsed_sig <- collapsed_results[collapsed_results$significant, c("comparison", "diff", "p_value")]
if (nrow(collapsed_sig) > 0) {
  print(kable(collapsed_sig, format = "simple", digits = 4))
} else {
  cat("  None\n")
}
```

## Visualization of Collapsed Data

```{r collapsed_visualization, fig.width=10, fig.height=6}
# Plot proportions with confidence intervals for collapsed data
collapsed_plot <- ggplot(collapsed_data, aes(x = reorder(model, proportion), y = proportion)) +
  geom_point(size = 4, color = "darkred") +
  geom_errorbar(aes(ymin = proportion - 1.96 * sqrt(proportion * (1 - proportion) / total),
                    ymax = proportion + 1.96 * sqrt(proportion * (1 - proportion) / total)),
                width = 0.2, size = 1, color = "darkred") +
  coord_flip() +
  theme_minimal() +
  labs(title = "Collapsed Data (Finke + 48 Novel) - Proportions with 95% CI",
       x = "Model",
       y = "Proportion Correct") +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"))

print(collapsed_plot)

# Create a comparison plot showing all three datasets

comparison_data <- bind_rows(
  finke_data %>% mutate(dataset = "Finke"),
  novel_data %>% mutate(dataset = "48 Novel"),
  collapsed_data %>% mutate(dataset = "Collapsed")
)

comparison_plot <- ggplot(comparison_data, aes(x = model, y = proportion, fill = dataset)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_minimal() +
  labs(title = "Comparison Across All Datasets",
       x = "Model",
       y = "Proportion Correct",
       fill = "Dataset") +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1))

print(comparison_plot)
```

## Heatmap for Collapsed Data

```{r collapsed_heatmap, fig.width=8, fig.height=8}
# Create matrix of p-values for collapsed data
collapsed_models <- collapsed_data$model
collapsed_pval_matrix <- matrix(NA, nrow = length(collapsed_models), ncol = length(collapsed_models))
rownames(collapsed_pval_matrix) <- collapsed_models
colnames(collapsed_pval_matrix) <- collapsed_models

for (i in 1:nrow(collapsed_results)) {
  row_idx <- which(collapsed_models == collapsed_results$model1[i])
  col_idx <- which(collapsed_models == collapsed_results$model2[i])
  collapsed_pval_matrix[row_idx, col_idx] <- collapsed_results$p_value[i]
  collapsed_pval_matrix[col_idx, row_idx] <- collapsed_results$p_value[i]
}

# Set diagonal to NA
diag(collapsed_pval_matrix) <- NA

# Set margins for better label display
par(mar = c(6, 6, 3, 2))

# Plot heatmap with same color palette
image(collapsed_pval_matrix, axes = FALSE, col = col_palette,
      main = "P-values Heatmap - Collapsed Data (Finke + 48 Novel)")
axis(1, at = seq(0, 1, length.out = length(collapsed_models)), labels = collapsed_models,
     las = 2, cex.axis = 0.8)  # las=2 makes labels perpendicular, cex.axis makes them smaller
axis(2, at = seq(0, 1, length.out = length(collapsed_models)), labels = collapsed_models,
     las = 2, cex.axis = 0.8)

# Add gray color for diagonal
for (i in 1:length(collapsed_models)) {
  x_pos <- (i - 1) / (length(collapsed_models) - 1)
  y_pos <- (i - 1) / (length(collapsed_models) - 1)
  rect(x_pos - 0.5 / (length(collapsed_models) - 1), y_pos - 0.5 / (length(collapsed_models) - 1),
       x_pos + 0.5 / (length(collapsed_models) - 1), y_pos + 0.5 / (length(collapsed_models) - 1),
       col = "gray80", border = NA)
}

# Add p-values to the plot
for (i in 1:nrow(collapsed_pval_matrix)) {
  for (j in 1:ncol(collapsed_pval_matrix)) {
    if (!is.na(collapsed_pval_matrix[i, j])) {
      x_pos <- (j - 1) / (ncol(collapsed_pval_matrix) - 1)
      y_pos <- (i - 1) / (nrow(collapsed_pval_matrix) - 1)
      text(x_pos, y_pos, sprintf("%.3f", collapsed_pval_matrix[i, j]), cex = 0.7)
    }
  }
}
```

## Export Results to CSV

```{r export}
# Combine all results
all_results <- rbind(finke_results, novel_48_results)

# Export to CSV
write.csv(all_results, "statistical_results/proportion_test_results.csv", row.names = FALSE)
cat("\nResults exported to 'proportion_test_results.csv'\n")

# Create a more detailed summary for export
detailed_summary <- all_results %>%
  mutate(
    prop1_percent = paste0(round(prop1 * 100, 1), "%"),
    prop2_percent = paste0(round(prop2 * 100, 1), "%"),
    diff_percent = paste0(round(diff * 100, 1), "%"),
    ci_95 = paste0("[", round(ci_lower, 3), ", ", round(ci_upper, 3), "]"),
    interpretation = case_when(
      p_value < 0.001 ~ "Highly significant (p < 0.001)",
      p_value < 0.01 ~ "Very significant (p < 0.01)",
      p_value < 0.05 ~ "Significant (p < 0.05)",
      p_value < 0.10 ~ "Marginally significant (p < 0.10)",
      TRUE ~ "Not significant"
    )
  ) %>%
  select(task, comparison, prop1_percent, prop2_percent, diff_percent,
         chi_squared, p_value, ci_95, interpretation)

# Export detailed summary
write.csv(detailed_summary, "statistical_results/proportion_test_detailed_summary.csv", row.names = FALSE)
cat("Detailed summary exported to 'proportion_test_detailed_summary.csv'\n")
```

